\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{booktabs}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\begin{document}

% ============================================================
% HEADER
% ============================================================
\begin{center}
    {\LARGE \textbf{Weekly Update --- Week 5}} \\[6pt]
    {\large CS161 --- Spring 2026}
\end{center}

\vspace{0.5em}

% ============================================================
% 1. Team Information
% ============================================================
\section{Team Information}

\begin{tabularx}{\textwidth}{@{}lX@{}}
    \textbf{Team Name:}       & Checkpoint (Team 2) \\
    \textbf{Team Members:}    & Omkar Podey, Anmol Rastogi \\
    \textbf{Team Leader:}     & Omkar Podey \\
    \textbf{Date of Submission:} & March 1, 2026 \\
\end{tabularx}

% ============================================================
% 2. Overall Team Objectives Completed
% ============================================================
\section{Overall Team Objectives Completed}

During Week~5, the team completed the following major objectives toward Sprint~1 (Foundation \& Infrastructure):

\begin{enumerate}[leftmargin=1.5em]
    \item \textbf{Product Requirements Document (PRD) finalized} --- Defined target personas, success metrics, all feature requirements, user flows, non-functional requirements, and scope constraints for the Checkpoint platform.

    \item \textbf{Sprint Plan created} --- Broke the project into three incremental sprints with user stories, technical tasks, deliverables, definitions of done, and a risk-mitigation matrix.

    \item \textbf{Technical architecture designed} --- Selected the tech stack (FastAPI + SQLAlchemy/SQLite for backend, React + Vite for frontend), designed the database schema (7~tables), defined the REST API surface under \texttt{/api/v1}, and planned the WebSocket layer with polling fallback.

    \item \textbf{Backend scaffolding and core implementation completed} --- Implemented the full backend structure including:
    \begin{itemize}[leftmargin=1.5em]
        \item Database models: User, Server, Channel, Message, Membership, Invite, ChannelMember.
        \item Routers: Auth, Servers, Channels, Messages, Invites, WebSocket.
        \item Service layer: Auth, Server, Channel, Message, Invite services.
        \item Pydantic schemas for request/response validation.
        \item WebSocket connection manager for real-time messaging.
        \item JWT-based authentication with secure password hashing.
    \end{itemize}

    \item \textbf{Frontend scaffolding and core UI completed} --- Built the full frontend component hierarchy:
    \begin{itemize}[leftmargin=1.5em]
        \item Auth components: Login form, Register form, Protected routes.
        \item Layout: Server sidebar, Channel list panel.
        \item Messaging: Message bubble, Message feed, Message input.
        \item Server management: Create server modal, Invite code modal, Server icon.
        \item Reusable UI: Button, Input, Loading spinner, Modal.
        \item Pages: Login, Register, Dashboard, Channel, Join Server.
        \item API layer: Axios client with auth, server, channel, message, and invite modules.
        \item Auth context and WebSocket hook for real-time updates.
    \end{itemize}
\end{enumerate}

% ============================================================
% 3. Individual Contributions
% ============================================================
\section{Individual Contributions}

\subsection{Omkar Podey}
\begin{itemize}[leftmargin=1.5em]
    \item Authored the Product Requirements Document (PRD).
    \item Designed the technical architecture and database schema.
    \item Implemented backend models, routers, services, and schemas for auth, servers, channels, messages, and invites.
    \item Set up the FastAPI project structure with SQLAlchemy ORM and SQLite.
    \item Implemented the WebSocket connection manager and real-time messaging endpoint.
    \item Configured JWT-based authentication flow.
\end{itemize}

\subsection{Anmol Rastogi}
\begin{itemize}[leftmargin=1.5em]
    \item Co-authored the Sprint Plan with user stories and task breakdowns.
    \item Built the React frontend scaffolding with Vite.
    \item Implemented authentication UI (Login, Register forms) and Protected Route component.
    \item Built the layout components (Sidebar, Channel list).
    \item Developed the messaging UI (Message bubble, feed, and input components).
    \item Created server management modals (Create Server, Invite Code).
    \item Implemented the API client layer and Auth context provider.
\end{itemize}

% ============================================================
% 4. Scrum Meetings
% ============================================================
\section{Scrum Meetings}

A total of \textbf{4 scrum meetings} were held during Week~5:

\begin{itemize}[leftmargin=1.5em]
    \item \textbf{2 in-class meetings} --- Used class time for sprint planning, task assignment, and architecture review.
    \item \textbf{2 outside-of-class meetings} --- Held virtually to coordinate on implementation progress, resolve integration questions between frontend and backend, and perform code review.
\end{itemize}

% ============================================================
% 5. Roadblocks / Blocking Issues
% ============================================================
\section{Roadblocks \& Blocking Issues}

\begin{enumerate}[leftmargin=1.5em]
    \item \textbf{WebSocket reliability on campus Wi-Fi} --- Initial testing showed occasional WebSocket disconnections on the university network. \textit{Mitigation:} Implementing a 10-second polling fallback as planned in the architecture.

    \item \textbf{Frontend--Backend integration testing} --- End-to-end integration between the React frontend and FastAPI backend has not yet been fully validated. CORS configuration and WebSocket token passing still need to be verified. \textit{Mitigation:} Scheduled as the next priority task.

    \item \textbf{No major blocking issues at this time} --- Development is on track for Sprint~1 completion. All user stories are in progress or completed.
\end{enumerate}

\end{document}
